---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# tutiempo

<!-- badges: start -->
<!-- badges: end -->

The `tutiempo` package provides meteorological data from
[Tutiempo.net](https://en.tutiempo.net) for

* Cambodia
* Lao PDR
* Malaysia
* Myanmar
* Philippines
* Thailand
* Vietnam

Until the 31st of December, 2016

## Installation

You can install the development version from
[GitHub](https://github.com/epix-project/tutiempo) with:

``` r
# install.packages("devtools")
devtools::install_github("epix-project/tutiempo")
```
## Example

The package contains 2 data frames:

* `meteo` contains de meteorological data;
* `stations` contains information about the climatic stations.

```{r example, eval = FALSE}
library(tutiempo)
data(meteo)
data(stations)
```

The common key between these two packages is the `station` variable.
